### 2017-10-25 Draft2/Appending.Dynamic.tex
Add predefined functions section, more work

\begin{description}
	\item[initial capacity] Denoted by $\VarInitCapacity$. The capacity of a dynamic a array when one item is appended to it.\\
	(The capacity of any dynamic array with size zero should be zero.)
	\item[growth factor] Denoted by $\VarGrowthFactor$. The factor by which the current capacity is multiplied to get the new capacity when $\VarList$ grows.
\end{description}

@@

			\State $\VarList.\FieldHead[\VarList.\FieldHeadSize] \gets item$
			\State $\VarList.\FieldSize \gets \VarList.\FieldSize + 1$
		\EndProcedure
		\Statex
		\Procedure{$\FuncGrow$}{$L$}
			\If{$\VarList.\FieldEmpty$}
				\State $\VarList.\FieldBuffer \gets \FuncNewArray(\VarInitCapacity)$
			\Else
				\State $new\ buf \gets \FuncNewArray(\VarList.\FieldSize \times \VarGrowthFactor)$
				\State $\FuncArrayCopy(source: \VarList.\FieldBuffer, dest: new\ buf, len: \VarList.\FieldSize)$
				\State $\VarList.\FieldBuffer \gets new\ buf$
			\EndIf
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

@@

Before I analyze the time complexity of $\FuncAppend$, I consider a different method for measuring its cost. Suppose I start with an empty list and $n$ elements are appended. How many times is an element stored in an array? I will term the answer to this question the \textbf{write cost} of $n$ appends, and denote it $\FuncWrites(n)$.

In the above code, one write is performed after the conditional, so it is apparent that $\FuncWrites(n) \geq n$ after $n$ appends. However, $\FuncGrow$ also does some writing, so in order to find a precise formula for $\FuncWrites(n)$, I need to analyze when $\FuncGrow$ is called. Consider the following lemma:

>>>>

\begin{description}
	\item[initial capacity] Denoted by $\VarInitCapacity$. The capacity of a dynamic a array when one item is appended to it.\\
	{\HdrNote} The capacity of any dynamic array with size zero should be zero.
	\item[growth factor] Denoted by $\VarGrowthFactor$. The factor by which the current capacity is multiplied to get the new capacity when $\VarList$ grows.
\end{description}

@@

			\State $\VarList.\FieldHead[\VarList.\FieldHeadSize] \gets item$
			\State $\VarList.\FieldSize \gets \VarList.\FieldSize + 1$
		\EndProcedure
		\Statex
		\Procedure{$\FuncGrow$}{$L$}
			\If{$\VarList.\FieldEmpty$}
				\State $\VarList.\FieldBuffer \gets \FuncNewArray(\VarInitCapacity)$
			\Else
				\State $new\ buf \gets \FuncNewArray(\VarList.\FieldSize \times \VarGrowthFactor)$
				\State $\FuncArrayCopy(\VarList.\FieldBuffer, new\ buf, \VarList.\FieldSize)$
				\State $\VarList.\FieldBuffer \gets new\ buf$
			\EndIf
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

@@

Before I analyze the time complexity of $\FuncAppend$, I consider a different method for measuring its cost. Suppose I start with an empty collection and $n$ elements are appended. How many times is an element stored in an array? I will term the answer to this question the \textbf{write cost} of $n$ appends, and denote it $\FuncWrites(n)$.

In the code for $\FuncAppend$, one array store is performed unconditionally, so it is apparent that $\FuncWrites(n) \geq n$ after $n$ appends. However, $\FuncGrow$ also does some writing, so in order to find a precise formula for $\FuncWrites(n)$, I need to analyze when $\FuncGrow$ is called. To do this, I use the following lemma:

% Bookmark
